Constraints on Cosmic Rays, Magnetic Fields, and Dark Matter from Gamma-Ray Observations of the Coma Cluster of Galaxies with VERITAS and \Fermi

### 2011-12-19 ms.tex
Some minor edits
Updated the author list

%\title{VHE Gamma-Ray Observations of the Coma Cluster of Galaxies with VERITAS}
%\title{Constraints on Cosmic-Ray Particle Populations, Magnetic Fields, and Dark Matter from VHE Gamma-Ray Observations of the Coma Cluster of Galaxies with VERITAS}
\title{Constraints on Cosmic Rays, Magnetic Fields, and Dark Matter from Gamma-Ray Observations of the Coma Cluster of Galaxies with VERITAS and \Fermi}
\author{
T. Arlen\altaffilmark{1},
M. Beilicke\altaffilmark{2},
W. Benbow\altaffilmark{3},
V. Bugaev\altaffilmark{2},
K. Byrum\altaffilmark{4},
A. Cannon\altaffilmark{5},
A. Cesarini\altaffilmark{6},
L. Ciupik\altaffilmark{7},
J. Dumm\altaffilmark{8},
G. Finnegan\altaffilmark{9},
L. Fortson\altaffilmark{8},
A. Furniss\altaffilmark{10},
N. Galante\altaffilmark{3},
G. Gyuk\altaffilmark{7},
P. Kaaret\altaffilmark{11},
N. Karlsson\altaffilmark{8,23},
D. Kieda\altaffilmark{9},
H. Krawczynski\altaffilmark{2},
G. Maier\altaffilmark{12},
P. Majumdar\altaffilmark{1},
S. McArthur\altaffilmark{2},
A. McCann\altaffilmark{13},
P. Moriarty\altaffilmark{14},
A. N. Otte\altaffilmark{15},
J. S. Perkins\altaffilmark{16,17},
M. Pohl\altaffilmark{18,12},
H. Prokoph\altaffilmark{12},
E. Roache\altaffilmark{3},
J. Ruppel\altaffilmark{18,12},
D. B. Saxon\altaffilmark{19},
G. H. Sembroski\altaffilmark{20},
C. Skole\altaffilmark{12},
I. Telezhinsky\altaffilmark{18,12},
G. Te\v{s}i\'{c}\altaffilmark{13},
S. Thibadeau\altaffilmark{2},
R. Welsing\altaffilmark{12}}

%%\email{nkarlsson@physics.umn.edu}
\and
\author{S. Federici\altaffilmark{12,18}, C. Pfrommer\altaffilmark{21,23},
A. Pinzke\altaffilmark{22}}

%% affiliations
\altaffiltext{1}{Department of Physics and Astronomy, University of California, Los Angeles, CA 90095, USA}
\altaffiltext{2}{Department of Physics, Washington University, St. Louis, MO 63130, USA}
\altaffiltext{3}{Fred Lawrence Whipple Observatory, Harvard-Smithsonian Center for Astrophysics, Amado, AZ 85645, USA}
\altaffiltext{4}{Argonne National Laboratory, 9700 S. Cass Avenue, Argonne, IL 60439, USA}
\altaffiltext{5}{School of Physics, University College Dublin, Belfield, Dublin 4, Ireland}
\altaffiltext{6}{School of Physics, National University of Ireland Galway, University Road, Galway, Ireland}
\altaffiltext{7}{Astronomy Department, Adler Planetarium and Astronomy Museum, Chicago, IL 60605, USA}
\altaffiltext{8}{School of Physics and Astronomy, University of Minnesota, Minneapolis, MN 55455, USA}
\altaffiltext{9}{Department of Physics and Astronomy, University of Utah, Salt Lake City, UT 84112, USA}
\altaffiltext{10}{Santa Cruz Institute for Particle Physics and Department of Physics, University of California, Santa Cruz, CA 95064, USA}
\altaffiltext{11}{Department of Physics and Astronomy, University of Iowa, Van Allen Hall, Iowa City, IA 52242, USA}
\altaffiltext{12}{DESY, Platanenallee 6, 15738 Zeuthen, Germany}
\altaffiltext{13}{Physics Department, McGill University, Montreal, QC H3A 2T8, Canada}
\altaffiltext{14}{Department of Life and Physical Sciences, Galway-Mayo Institute of Technology, Dublin Road, Galway, Ireland}
\altaffiltext{15}{School of Physics \& Center for Relativistic Astrophysics, Georgia Institute of Technology, 837 State Street NW, Atlanta, GA 30332-0430}
\altaffiltext{16}{CRESST and Astroparticle Physics Laboratory NASA/GSFC, Greenbelt, MD 20771, USA.}
\altaffiltext{17}{University of Maryland, Baltimore County, 1000 Hilltop Circle, Baltimore, MD 21250, USA.}
\altaffiltext{18}{Institut f\"ur Physik und Astronomie, Universit\"at Potsdam, 14476 Potsdam-Golm,Germany}
\altaffiltext{19}{Department of Physics and Astronomy and the Bartol Research Institute, University of Delaware, Newark, DE 19716, USA}
\altaffiltext{20}{Department of Physics, Purdue University, West Lafayette, IN 47907, USA }
\altaffiltext{21}{Heidelberg Institute for Theoretical Studies, Schloss-Wolfsbrunnenweg 35, D-69118 Heidelberg, Germany}
\altaffiltext{22}{Department of Physics, University of California, Santa Barbara, CA 93106, USA}
\altaffiltext{23}{Corresponding authors: N. Karlsson, nkarlsson@physics.umn.edu \& C. Pfrommer, christoph.pfrommer@h-its.org}

%%\journalinfo{The Astrophysical Journal}
%%\submitted{preprint}

@@

\begin{enumerate}
\item
Given a model for the magnetic field with $\alpha_B$ and an initial guess for $B_0$, we determine
the profile of the relative CR pressure, $X_{\CR}(r)$, by matching the hadronically produced
synchrotron emission to the observed radio halo emission over the entire extent. To 
this end, we de-project the fit to the surface brightness profile of Eqn.~\ref{beta} (using an Abel
integral equation, see Appendix of \citealt{article:PfrommerEnsslin:2004b}) yielding the radio
emissivity,

@@

\item Inverse Compton cooling of CR electrons on CMB photons introduces a characteristic scale of
  $B_{\rmn{CMB}}\simeq 3.2\,\mu$G which imprints as a non-linearity on the synchrotron emissivity as
  a function of magnetic field strength (see Eqn.~(\ref{eq:Lnu})). Hence we have to iterate through
  the previous steps until our solution for the minimum magnetic field $B_{0}$ is converged.
\end{enumerate}

@@

\begin{deluxetable}{lccccccccc}
\tablecolumns{10}
\tablewidth{0pc}
\tablecaption{VERITAS flux upper limits for different regions of interest in the Coma cluster of
galaxies and surroundings}
\rotate
\tablehead{
\colhead{Source} & 
\colhead{RoI\tablenotemark{a} [deg]} & 
\colhead{$N_{S}$\tablenotemark{b}} & 
\colhead{S\tablenotemark{c} [$\sigma$]} &
\multicolumn{6}{c}{Flux U.L.\tablenotemark{d}} \\
\colhead{} & 
\colhead{} & 
\colhead{} & 
\colhead{} &
\multicolumn{2}{c}{$\alpha=2.1$} &
\multicolumn{2}{c}{$\alpha=2.3$} &
\multicolumn{2}{c}{$\alpha=2.5$}
}
\startdata
Core & 0 & 17 & 0.84 & 2.59 & (0.78\%) & 2.78 & (0.83\%) & 2.97 & (0.89\%) \\
& 0.2 & -41 & -1.0 & 1.96 & (0.59\%)  & 2.09 & (0.63\%) & 2.21 & (0.66\%) \\
& 0.4 & -26 & -0.30 & 4.44 & (1.3\%)  & 4.74 & (1.4\%) & 5.02 & (1.5\%)\\
NGC 4889 & 0 & 3 & 0.14 & - & - & 1.85 & (0.55\%)  & - & - \\
NGC 4874 & 0 & -14 & -0.71 & - & - &  1.51 & (0.45\%)  & - & - \\
NGC 4921 & 0 & -4 & -0.23 & - & - &  2.41 & (0.72\%)  & - & -
\enddata
\tablenotetext{a}{Intrinsic source radius (zero means point source), which is convolved with the
analysis PSF.}
\tablenotetext{b}{Event counts in the source region.}
\tablenotetext{c}{Statistical significance calculated according to \citet{article:LiMa:1983}.}
\tablenotetext{d}{99\% confidence level upper limit in units of $10^{-8}$ ph. m$^{-2}$ s$^{-1}$
calculated according to \citet{article:Rolke_etal:2005} above an energy threshold of 220 GeV, with
corresponding fluxes in percent of the steady Crab Nebula flux in parenthesis.}
\label{table:results}
\end{deluxetable}

@@

\begin{deluxetable}{cccccc}
\tablecolumns{6}
\tablewidth{0pc}
\tablecaption{Constraints on the relative CR pressure in the Coma cluster core (simplified, isobaric
analytic model) for different spatial extensions and predicted fluxes for the energy bands 1-3 GeV
and $>220$~GeV (simulation-based model).}
\rotate
\tabletypesize{\small}
\tablehead{
\colhead{RoI\tablenotemark{a} [deg]} 
& \multicolumn{3}{c}{analytic model: $X_{\CR,\,\rmn{max}}~[\%]$\tablenotemark{b} }
& \colhead{$F_{\gamma,\rmn{sim}}(E)$\tablenotemark{c}}
& \colhead{$F_{\rmn{UL}}/F_{\gamma,\rmn{sim}}(>E)$\tablenotemark{d}} \\
& \colhead{$\alpha=2.1$} & \colhead{$\alpha=2.3$} & \colhead{$\alpha=2.5$} & & 
}
\startdata
\multicolumn{6}{c}{VERITAS constraints:}\\
\hline
0 & 10 & 23 & 97 & 1.9 & 14.8\\
0.2 & 4.8 & 10 & 43 & 2.9 & 7.2\\
0.4 & 6.7 & 15 & 62 & 4.4 & 10.8\\
\cutinhead{\Fermi constraints:}
0 & 5.2 & 3.5 & 4.7 & 1.4 & 1.96\\
0.2 & 3.5 & 2.4 & 3.1 & 2.1 & 1.46\\
0.4 & 2.5 & 1.7 & 2.3 & 3.2 & 1.10\\
\enddata
\tablenotetext{a}{Intrinsic source radius (zero means point source), which is convolved with the
analysis PSF.}
\tablenotetext{b}{Constraint on the relative CR pressure,
$X_{\CR} = \expval{P_\CR}/ \expval{P_\rmn{th}}$, which was assumed to be constant through the
cluster and calculated according to \citet{article:PfrommerEnsslin:2004b}.}
\tablenotetext{c}{Integrated gamma-ray flux from the simulation-based analytic model by
\citet{article:PinzkePfrommer:2010}: above $E=220~\rmn{GeV}$ in units of $10^{-9}$ ph. m$^{-2}$
s$^{-1}$ for VERITAS and between $E=1-3~\rmn{GeV}$ in units of $10^{-6}$ ph. m$^{-2}$ s$^{-1}$ for
Fermi.} 
\tablenotetext{d}{Ratio of flux upper limits ($F_{\rmn{UL}}$) to the integrated gamma-ray flux
from the simulation-based analytic model: in VERITAS band above $E=220~\rmn{GeV}$ an $\alpha=2.3$
is assumed for the U.L., and in \Fermi band between $E=1-3$ GeV an $\alpha=2.1$ is assumed for the
U.L.}
\label{table:constraints_simple}
\end{deluxetable}

@@

\begin{deluxetable}{ccccccc}
\tablecolumns{7}
\tablewidth{0pc}
\tablecaption{Minimum gamma-ray fluxes in the hadronic model of radio halos, where the
radio-emitting electrons are secondaries from CR interactions and corresponding minimum relative
CR pressures for Coma}
\rotate
\tabletypesize{\small}
\tablehead{
\colhead{RoI\tablenotemark{a} [deg]} 
& \multicolumn{3}{c}{$F_{\gamma,\,\rmn{min}}(>E)$\tablenotemark{b}} 
& \multicolumn{3}{c}{$X_{\CR,\,\rmn{min}}~[\%]$\tablenotemark{c} } \\
& \colhead{$\alpha=2.1$} & \colhead{$\alpha=2.3$} & \colhead{$\alpha=2.5$}
& \colhead{$\alpha=2.1$} & \colhead{$\alpha=2.3$} & \colhead{$\alpha=2.5$}
}
\startdata
\multicolumn{7}{c}{VERITAS energy range, $E>220$~GeV:}\\
\hline
0.13 & 1.6 & 0.7 & 0.3 & 0.067 & 0.061 & 0.11 \\
0.2  & 3.1 & 1.4 & 0.6 & 0.078 & 0.072 & 0.13 \\
0.4  & 6.3 & 2.8 & 1.3 & 0.098 & 0.090 & 0.16 \\
\cutinhead{\Fermi energy range, 1--3~GeV:}
0.13 & ~~3.5 & ~~4.8 & ~~6.4 & 0.067 & 0.061 & 0.11 \\
0.2  & ~~6.8 & ~~9.3 &  12.5 & 0.078 & 0.072 & 0.13 \\
0.4  &  13.5 & 18.6  &  25.0 & 0.098 & 0.090 & 0.16 \\
\enddata
\tablenotetext{a}{Intrinsic source radius (zero means point source), which is convolved with the
analysis PSF.}
\tablenotetext{b}{Minimum gamma-ray flux of the hadronic model described in \S~\ref{sec:Fmin}. 
Values are in units of $10^{-10}$ ph. m$^{-2}$ s$^{-1}$ (VERITAS energy range) and $10^{-8}$ ph.
m$^{-2}$ s$^{-1}$ (\Fermi energy range).}
\tablenotetext{c}{Minimum relative CR pressure, $X_{\CR,\,\rmn{min}}$, in the hadronic model
described in \S~\ref{sec:Fmin}. For simplicity, we duplicate $X_{\CR,\,\rmn{min}}$ for the VERITAS
and \Fermi constraints: for a given realization of the CR pressure (and a magnetic field model
which is trivial here as we assume $B \gg B_\rmn{CMB}$), we can derive the radio flux as well as
gamma-ray fluxes in various bands (1--3 GeV, $>220$ GeV).}
\label{table:constraints}
\end{deluxetable}

>>>>

%\title{VHE Gamma-Ray Observations of the Coma Cluster of Galaxies with VERITAS}
%\title{Constraints on Cosmic-Ray Particle Populations, Magnetic Fields, and Dark Matter from VHE Gamma-Ray Observations of the Coma Cluster of Galaxies with VERITAS}
\title{Constraints on Cosmic Rays, Magnetic Fields, and Dark Matter from Gamma-Ray Observations of the Coma Cluster of Galaxies with VERITAS and \Fermi}
\author{
T. Arlen\altaffilmark{1},
M. Beilicke\altaffilmark{2},
W. Benbow\altaffilmark{3},
V. Bugaev\altaffilmark{2},
K. Byrum\altaffilmark{4},
A. Cannon\altaffilmark{5},
A. Cesarini\altaffilmark{6},
L. Ciupik\altaffilmark{7},
E. Collins-Hughes\altaffilmark{5},
W. Cui\altaffilmark{8},
R. Dickherber\altaffilmark{2},
J. Dumm\altaffilmark{9},
Q. Feng\altaffilmark{8},
G. Finnegan\altaffilmark{10},
L. Fortson\altaffilmark{9},
A. Furniss\altaffilmark{11},
N. Galante\altaffilmark{3},
J. Grube\altaffilmark{7},
G. Gyuk\altaffilmark{7},
H. Huan\altaffilmark{12},
G. Hughes\altaffilmark{13},
T. B. Humensky\altaffilmark{14},
P. Kaaret\altaffilmark{15},
N. Karlsson\altaffilmark{9,27},
Y. Khassen\altaffilmark{5},
D. Kieda\altaffilmark{10},
H. Krawczynski\altaffilmark{2},
G. Maier\altaffilmark{13},
P. Majumdar\altaffilmark{1},
S. McArthur\altaffilmark{2},
A. McCann\altaffilmark{16},
P. Moriarty\altaffilmark{17},
M. Orr\altaffilmark{18},
A. N. Otte\altaffilmark{19},
J. S. Perkins\altaffilmark{20,21},
M. Pohl\altaffilmark{22,13},
H. Prokoph\altaffilmark{13},
P. T. Reynolds\altaffilmark{23},
E. Roache\altaffilmark{3},
J. Ruppel\altaffilmark{22,13},
D. B. Saxon\altaffilmark{24},
G. H. Sembroski\altaffilmark{8},
C. Skole\altaffilmark{13},
A. W. Smith\altaffilmark{10},
I. Telezhinsky\altaffilmark{22,13},
G. Te\v{s}i\'{c}\altaffilmark{16},
S. Thibadeau\altaffilmark{2},
M. Vivier\altaffilmark{24},
J. E. Ward\altaffilmark{5},
R. Welsing\altaffilmark{13}
}

\and
\author{S. Federici\altaffilmark{13,22}, C. Pfrommer\altaffilmark{25,27},
A. Pinzke\altaffilmark{26}}

\altaffiltext{1}{Department of Physics and Astronomy, University of California, Los Angeles, CA 90095, USA}
\altaffiltext{2}{Department of Physics, Washington University, St. Louis, MO 63130, USA}
\altaffiltext{3}{Fred Lawrence Whipple Observatory, Harvard-Smithsonian Center for Astrophysics, Amado, AZ 85645, USA}
\altaffiltext{4}{Argonne National Laboratory, 9700 S. Cass Avenue, Argonne, IL 60439, USA}
\altaffiltext{5}{School of Physics, University College Dublin, Belfield, Dublin 4, Ireland}
\altaffiltext{6}{School of Physics, National University of Ireland Galway, University Road, Galway, Ireland}
\altaffiltext{7}{Astronomy Department, Adler Planetarium and Astronomy Museum, Chicago, IL 60605, USA}
\altaffiltext{8}{Department of Physics, Purdue University, West Lafayette, IN 47907, USA }
\altaffiltext{9}{School of Physics and Astronomy, University of Minnesota, Minneapolis, MN 55455, USA}
\altaffiltext{10}{Department of Physics and Astronomy, University of Utah, Salt Lake City, UT 84112, USA}
\altaffiltext{11}{Santa Cruz Institute for Particle Physics and Department of Physics, University of California, Santa Cruz, CA 95064, USA}
\altaffiltext{12}{Enrico Fermi Institute, University of Chicago, Chicago, IL 60637, USA}
\altaffiltext{13}{DESY, Platanenallee 6, 15738 Zeuthen, Germany}
\altaffiltext{14}{Physics Department, Columbia University, New York, NY 10027, USA}
\altaffiltext{15}{Department of Physics and Astronomy, University of Iowa, Van Allen Hall, Iowa City, IA 52242, USA}
\altaffiltext{16}{Physics Department, McGill University, Montreal, QC H3A 2T8, Canada}
\altaffiltext{17}{Department of Life and Physical Sciences, Galway-Mayo Institute of Technology, Dublin Road, Galway, Ireland}
\altaffiltext{18}{Department of Physics and Astronomy, Iowa State University, Ames, IA 50011, USA}
\altaffiltext{19}{School of Physics \& Center for Relativistic Astrophysics, Georgia Institute of Technology, 837 State Street NW, Atlanta, GA 30332-0430}
\altaffiltext{20}{CRESST and Astroparticle Physics Laboratory NASA/GSFC, Greenbelt, MD 20771, USA.}
\altaffiltext{21}{University of Maryland, Baltimore County, 1000 Hilltop Circle, Baltimore, MD 21250, USA.}
\altaffiltext{22}{Institut f\"ur Physik und Astronomie, Universit\"at Potsdam, 14476 Potsdam-Golm,Germany}
\altaffiltext{23}{Department of Applied Physics and Instrumentation, Cork Institute of Technology, Bishopstown, Cork, Ireland}
\altaffiltext{24}{Department of Physics and Astronomy and the Bartol Research Institute, University of Delaware, Newark, DE 19716, USA}

% Christoph, Anders and Simone:
\altaffiltext{25}{Heidelberg Institute for Theoretical Studies, Schloss-Wolfsbrunnenweg 35, D-69118 Heidelberg, Germany}
\altaffiltext{26}{Department of Physics, University of California, Santa Barbara, CA 93106, USA}
\altaffiltext{27}{Corresponding authors: N. Karlsson, nkarlsson@physics.umn.edu \& C. Pfrommer, christoph.pfrommer@h-its.org}

%%\email{nkarlsson@physics.umn.edu}
%%\journalinfo{The Astrophysical Journal}
%%\submitted{preprint}

@@

\begin{enumerate}
\item
Given a model for the magnetic field with $\alpha_B$ and an initial guess for $B_0$, we determine
the profile of the relative CR pressure, $X_{\CR}(r)$, by matching the hadronically produced
synchrotron emission to the observed radio halo emission over the entire extent. To 
this end, we de-project the fit to the surface brightness profile of Eq. \ref{beta} (using an Abel
integral equation, see Appendix of \citealt{article:PfrommerEnsslin:2004b}) yielding the radio
emissivity,

@@

\item Inverse Compton cooling of CR electrons on CMB photons introduces a characteristic scale of
  $B_{\rmn{CMB}}\simeq 3.2\,\mu$G which imprints as a non-linearity on the synchrotron emissivity as
  a function of magnetic field strength (see Eq. (\ref{eq:Lnu})). Hence we have to iterate through
  the previous steps until our solution for the minimum magnetic field $B_{0}$ is converged.
\end{enumerate}

@@

\begin{deluxetable}{lccccccccc}
\tablecolumns{10}
\tablewidth{0pc}
\tablecaption{VERITAS flux upper limits for different regions of interest in the Coma cluster of
galaxies and surroundings}
\rotate
\tablehead{
\colhead{Source} & 
\colhead{RoI\tablenotemark{a} [deg]} & 
\colhead{$N_{S}$\tablenotemark{b}} & 
\colhead{S\tablenotemark{c} [$\sigma$]} &
\multicolumn{6}{c}{Flux U.L.\tablenotemark{d}} \\
\colhead{} & 
\colhead{} & 
\colhead{} & 
\colhead{} &
\multicolumn{2}{c}{$\alpha=2.1$} &
\multicolumn{2}{c}{$\alpha=2.3$} &
\multicolumn{2}{c}{$\alpha=2.5$}
}
\startdata
Core & 0 & 17 & 0.84 & 2.59 & (0.78\%) & 2.78 & (0.83\%) & 2.97 & (0.89\%) \\
& 0.2 & -41 & -1.0 & 1.96 & (0.59\%)  & 2.09 & (0.63\%) & 2.21 & (0.66\%) \\
& 0.4 & -26 & -0.30 & 4.44 & (1.3\%)  & 4.74 & (1.4\%) & 5.02 & (1.5\%)\\
NGC 4889 & 0 & 3 & 0.14 & - & - & 1.85 & (0.55\%)  & - & - \\
NGC 4874 & 0 & -14 & -0.71 & - & - &  1.51 & (0.45\%)  & - & - \\
NGC 4921 & 0 & -4 & -0.23 & - & - &  2.41 & (0.72\%)  & - & -
\enddata
\tablenotetext{a}{Intrinsic source radius (zero means point source), which is convolved with the
gamma-ray PSF.}
\tablenotetext{b}{Event counts in the source region.}
\tablenotetext{c}{Statistical significance calculated according to \citet{article:LiMa:1983}.}
\tablenotetext{d}{99\% confidence level upper limit in units of $10^{-8}$ ph. m$^{-2}$ s$^{-1}$
calculated according to \citet{article:Rolke_etal:2005} above an energy threshold of 220 GeV, with
corresponding fluxes in percent of the steady Crab Nebula flux in parenthesis.}
\label{table:results}
\end{deluxetable}

@@

\begin{deluxetable}{cccccc}
\tablecolumns{6}
\tablewidth{0pc}
\tablecaption{Constraints on the relative CR pressure in the Coma cluster core (simplified, isobaric
analytic model) for different spatial extensions and predicted fluxes for the energy bands 1-3 GeV
and $>220$~GeV (simulation-based model).}
\rotate
\tabletypesize{\small}
\tablehead{
\colhead{RoI\tablenotemark{a} [deg]} 
& \multicolumn{3}{c}{analytic model: $X_{\CR,\,\rmn{max}}~[\%]$\tablenotemark{b} }
& \colhead{$F_{\gamma,\rmn{sim}}(E)$\tablenotemark{c}}
& \colhead{$F_{\rmn{UL}}/F_{\gamma,\rmn{sim}}(>E)$\tablenotemark{d}} \\
& \colhead{$\alpha=2.1$} & \colhead{$\alpha=2.3$} & \colhead{$\alpha=2.5$} & & 
}
\startdata
\multicolumn{6}{c}{VERITAS constraints:}\\
\hline
0 & 10 & 23 & 97 & 1.9 & 14.8\\
0.2 & 4.8 & 10 & 43 & 2.9 & 7.2\\
0.4 & 6.7 & 15 & 62 & 4.4 & 10.8\\
\cutinhead{\Fermi constraints:}
0 & 5.2 & 3.5 & 4.7 & 1.4 & 1.96\\
0.2 & 3.5 & 2.4 & 3.1 & 2.1 & 1.46\\
0.4 & 2.5 & 1.7 & 2.3 & 3.2 & 1.10\\
\enddata
\tablenotetext{a}{Intrinsic source radius (zero means point source), which is convolved with the
gamma-ray PSF.}
\tablenotetext{b}{Constraint on the relative CR pressure,
$X_{\CR} = \expval{P_\CR}/ \expval{P_\rmn{th}}$, which was assumed to be constant through the
cluster and calculated according to \citet{article:PfrommerEnsslin:2004b}.}
\tablenotetext{c}{Integrated gamma-ray flux from the simulation-based analytic model by
\citet{article:PinzkePfrommer:2010}: above $E=220~\rmn{GeV}$ in units of $10^{-9}$ ph. m$^{-2}$
s$^{-1}$ for VERITAS and between $E=1-3~\rmn{GeV}$ in units of $10^{-6}$ ph. m$^{-2}$ s$^{-1}$ for
Fermi.} 
\tablenotetext{d}{Ratio of flux upper limits ($F_{\rmn{UL}}$) to the integrated gamma-ray flux
from the simulation-based analytic model: in VERITAS band above $E=220~\rmn{GeV}$ an $\alpha=2.3$
is assumed for the U.L., and in \Fermi band between $E=1-3$ GeV an $\alpha=2.1$ is assumed for the
U.L.}
\label{table:constraints_simple}
\end{deluxetable}

@@

\begin{deluxetable}{ccccccc}
\tablecolumns{7}
\tablewidth{0pc}
\tablecaption{Minimum gamma-ray fluxes in the hadronic model of radio halos, where the
radio-emitting electrons are secondaries from CR interactions and corresponding minimum relative
CR pressures for Coma}
\rotate
\tabletypesize{\small}
\tablehead{
\colhead{RoI\tablenotemark{a} [deg]} 
& \multicolumn{3}{c}{$F_{\gamma,\,\rmn{min}}(>E)$\tablenotemark{b}} 
& \multicolumn{3}{c}{$X_{\CR,\,\rmn{min}}~[\%]$\tablenotemark{c} } \\
& \colhead{$\alpha=2.1$} & \colhead{$\alpha=2.3$} & \colhead{$\alpha=2.5$}
& \colhead{$\alpha=2.1$} & \colhead{$\alpha=2.3$} & \colhead{$\alpha=2.5$}
}
\startdata
\multicolumn{7}{c}{VERITAS energy range, $E>220$~GeV:}\\
\hline
0.13 & 1.6 & 0.7 & 0.3 & 0.067 & 0.061 & 0.11 \\
0.2  & 3.1 & 1.4 & 0.6 & 0.078 & 0.072 & 0.13 \\
0.4  & 6.3 & 2.8 & 1.3 & 0.098 & 0.090 & 0.16 \\
\cutinhead{\Fermi energy range, 1--3~GeV:}
0.13 & ~~3.5 & ~~4.8 & ~~6.4 & 0.067 & 0.061 & 0.11 \\
0.2  & ~~6.8 & ~~9.3 &  12.5 & 0.078 & 0.072 & 0.13 \\
0.4  &  13.5 & 18.6  &  25.0 & 0.098 & 0.090 & 0.16 \\
\enddata
\tablenotetext{a}{Intrinsic source radius (zero means point source), which is convolved with the
gamma-ray PSF.}
\tablenotetext{b}{Minimum gamma-ray flux of the hadronic model described in \S~\ref{sec:Fmin}. 
Values are in units of $10^{-10}$ ph. m$^{-2}$ s$^{-1}$ (VERITAS energy range) and $10^{-8}$ ph.
m$^{-2}$ s$^{-1}$ (\Fermi energy range).}
\tablenotetext{c}{Minimum relative CR pressure, $X_{\CR,\,\rmn{min}}$, in the hadronic model
described in \S~\ref{sec:Fmin}. For simplicity, we duplicate $X_{\CR,\,\rmn{min}}$ for the VERITAS
and \Fermi constraints: for a given realization of the CR pressure (and a magnetic field model
which is trivial here as we assume $B \gg B_\rmn{CMB}$), we can derive the radio flux as well as
gamma-ray fluxes in various bands (1--3 GeV, $>220$ GeV).}
\label{table:constraints}
\end{deluxetable}
